\tool: Revisiting BadUSB with Type-C

### 2021-03-20 WOOT/Files/introduction.tex
Limitations in intro
revised paper round 2

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
victim's \ac{GUI} during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.  
Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers participated in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

>>>>

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  
Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as the products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the
victim's \ac{GUI} during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers participated in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}
